Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-11 main_paper.tex
Tweak Assumption 2.
We don't expliclty impose boundedness of the kernel and don't explain
what kappa is.

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval.
\end{assumption}
To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
define the scaled and truncated kernel functions
\begin{align*}
  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \geq 0\} &
  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x < 0\}
\intertext{and}
  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \geq 0\} &
  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x < 0\}.
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice. Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.\footnote{%
  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
  would not affect our proofs.} %
For simplicity, however, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

>>>>

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive, bounded, and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval for some $\kappa > 0$.
\end{assumption}
To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
define the scaled and truncated kernel functions
\begin{align*}
  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \geq 0\} &
  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x < 0\}
\intertext{and}
  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \geq 0\} &
  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x < 0\}.
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice. Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.\footnote{%
  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
  would not affect our proofs.} %
For simplicity, however, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.
